---
title: "p8105_hw6_problem2"
author: "Chuhan Zhou & He Jin"
date: "11/15/2017"
output: 
  flexdashboard::flex_dashboard:
    orientation: row
  runtime: shiny
---

```{r setup, include=FALSE,message = FALSE}
library(flexdashboard)
library(tidyverse)
library(janitor)
library(stringr)
library(forcats)
library(viridis)
library(plotly)
library(shiny)

instacart = read_csv("../data/orders_train_allvars.csv") %>%
  clean_names() 
```

Column {.sidebar}
-----------------------------------------------------------------------

```{r sliderinput}
# selectInput widget
department = instacart %>% distinct(department) %>% pull()
selectInput("department_choice", label = h3("Select department"),
            choices = department, selected = "alcohol")

# sliderInput widget
sliderInput("order_number", label = h3("Choose the range of order number"), min = 1000, 
        max = 500000, value = c(1000, 500000))

# radioButtons widget

order_time = instacart %>% distinct(order_dow) %>% pull()
radioButtons("order_time", label = h3("Choose the order time"),
    choices = order_time, 
    selected = "0")
```


Row
-----------------------------------------------------------------------

### Chart A

```{r}
renderPlotly({
  instacart %>% 
  group_by(department) %>%
  summarize(items_ordered = n()) %>%
  mutate(department = as.factor(department),
         department = fct_reorder(department, items_ordered)) %>% 
  filter( items_ordered %in% input$order_number[1]:input$order_number[2]) %>%
  plot_ly(x = ~department, y = ~items_ordered, color = ~department, type = "bar")
})
```
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Chart B

```{r}
renderPlotly({
  instacart %>%
  group_by(department,aisle) %>%
  summarize(items_ordered = n()) %>%
  mutate(aisle = fct_reorder(aisle, items_ordered)) %>%
  filter( department == input$department_choice) %>%
  plot_ly(x = ~aisle, y = ~items_ordered, type = "scatter",              mode = "markers",
          alpha = 0.5, 
          color = ~aisle)
})
```

### Chart C

```{r}
renderPlotly({
  instacart %>%
  filter(order_dow == input$order_time) %>%
 group_by(order_dow,department) %>%
#  summarize(mean_hour = mean(order_hour_of_day)) %>%
#  select(department,mean_hour) %>%

  plot_ly(x = ~department, y = ~order_hour_of_day, color = ~department, type = "box", colors = "Set2")


})
  
```

